### 2022-10-22 article/article.tex
update

\documentclass[draft=True]{revtex4-2}
\newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{R})}}}
\newcommand{\ztrue}{\ensuremath{\cos{(\theta_z^{T})}}}
\newcommand{\emm}{\ensuremath{\epsilon_{\mu\mu}}}
\newcommand{\emt}{\ensuremath{\epsilon_{\mu\tau}}}
\newcommand{\eet}{\epsilon_{e\tau}}
\newcommand{\eem}{\epsilon_{e\mu}}
\newcommand{\ett}{\ensuremath{\epsilon_{\tau\tau}}}
\newcommand{\ep}{\ensuremath{\epsilon^\prime}}
\renewcommand{\ne}{\nu_e}
\newcommand{\Ereco}{E^{R}}
\newcommand{\Etrue}{E^{T}}
\newcommand{\nm}{\nu_\mu}
\newcommand{\nt}{\nu_\tau}
\newcommand{\ane}{\bar\nu_e}
\newcommand{\anm}{\bar\nu_\mu}               
\newcommand{\ant}{\bar\nu_\tau}
\newcommand{\dm}{\Delta m^2_{31}}
\newcommand{\sth}{\sin^2(2\theta_{23})}

\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\begin{document}
\section{Formalism of non-standard interactions}
Non-standard interactions are sub-leading contributions to neutrino flavor transitions arising from neutrino interactions not considered in the Standard Model.
We consider matter NSIs arising from the neutral current NSIs, which exclude production 
and detection effects. An effective four-fermion Lagrangian for this type of interaction can be written as
\begin{align}
   \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align}
where NC denotes the neutral current interaction with 
$f \in \{e,u,d\}$, and $P_X$ is the chirality projection operators with $X \in \{L,R\}$.

@@

We have no independent sensitivity for the chirality of $\epsilon^{fX}$, so we sum over these to obtain the vectorial parameter as $\epsilon^{fV}_{\alpha\beta} = \epsilon^{fL}_{\alpha\beta}+ \epsilon^{fR}_{\alpha\beta}$.
Moreover, we normalize the fermion number density $n_f$ by
the electron number density $n_e$. Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
so we use the relations $n_u/n_e \simeq n_d/n_e \simeq 3$.
The effective NSI parameters in matter now take the form
\begin{align} \label{eq:epsilon}
    \epsilon_{\alpha\beta} &= \sum_{f,X} \frac{n_f}{n_e} \epsilon^{fX}_{\alpha\beta} \nonumber \\
                           &= \epsilon_{\alpha\beta}^{eV} + 3\,\epsilon_{\alpha\beta}^{uV} + 3\,\epsilon_{\alpha\beta}^{dV}
\end{align}
We note that our definition of $\epsilon_{\alpha\beta}$ differs from e.g. \cite{deepcoreNSI}, where the quark number density is used to normalize
the parameters.

@@

To propagate the neutrino states through the Earth, we solve the Schrödinger equation with the Hamiltonian from Eq.~\ref{eq:H_NSI}. 
The Earth density profile is taken from the PREM~\cite{PREM}, and we do not consider neutrino absorption.
The baseline for a given trajectory is determined using an average neutrino production height of 15 km and an Earth radius of 6371 km.
Thus, matter oscillations introduce a zenith angle dependence in two areas. Firstly, the matter potential depends on the matter density through the
neutrino propagates. A neutrino with $\cos{\theta_z} < -0.87$ will traverse through the dense Earth core, whereas a mantle-crossing neutrino 
with $\cos{\theta_z} > -0.87$ will not. Secondly, the zenith angle also alters the baseline through which a neutrino undergoes matter oscillations.
After this, we are ready to study the NSI effect on probability level.
%TODO: add more here? are there more effects than just absoption missing? justify absorption missing?

\subsection{NSI phenomenology at probability level}\label{sec:nsiProbEffects}
% Since neutrinos and antineutrinos have different cross sections, they are treated separately in the detector simulations. 
% However, for the purpose of qualitatively elucidating the NSI effect in this subsection, we take the effective area of $\nm$ and $\anm$ to be equal. 
% Thus, we simply add the neutrino to the antineutrino contributions in both Fig.~\ref{fig:nsi_probs} and Fig.~\ref{fig:flux_ratio}.

@@

% Due to the lightness of $\Delta m^2_{21}$, the $e$ channel has no resonance in the \si{\GeV} range. Thus, the only impact that 
% the NSI parameters considered here can have on any $\nu_e$ probability is shifting, and this only occurs when the requirements for the `double effect'
% are met. So except for the survival probability $P_{ee}$, any NSI parameter whose sector does not match the probability sector will not drastically affect it. 
% Thus, the only off-diagonal NSI parameters that strongly affect the transition probabilities $P_{\alpha\beta}$ are $\epsilon_{\gamma\beta}$,
% while the survival probabilities $P_{\alpha\alpha}$ are only strongly affected by $\epsilon_{\alpha\beta}$.
%TODO: make this clearer and give conclusion. Maybe also test for lower E around dm21 resonance. Add about realness and CP-invariance
\begin{figure}
   \includegraphics[width=0.85\textwidth]{figures/probabilities.pdf}
   \caption{}\label{fig:nsi_probs}
\end{figure}

@@

\begin{figure}[!tb]
   \begin{center}
      \includegraphics[width=0.8\linewidth]{figures/flux_ratio.pdf}
   \end{center}
   \caption{Ratio of detector NSI to SI atmospheric $\nu_\mu + \bar{\nu}_\mu$ fluxes expressed as $(\phi_{\nu_\mu}^{NSI} + \phi_{\bar\nu_\mu}^{NSI})/(\phi_{\nu_\mu}^{SI} + \phi_{\bar\nu_\mu}^{SI})$.
   We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
   Left (right) panel shows the flux ratio in the energy range in which 99\% of the simulated DeepCore (IceCube) events are contained.
   }\label{fig:flux_ratio}
\end{figure}%TODO: make prettier cmap

\section{Detector formalism}
The IceCube Neutrino Observatory is a gigaton Cherenkov detector located within Antarctic ice near the Geographic 
South Pole. It consists of 5160 individual digital optical modules situated on 86 strings, which detect Cherenkov light emitted by charged leptons
from neutrino events. We distinguish between two interaction topologies: track- and cascade-like events. Track-like events originate mainly
from muons originating from $\nm$ CC interactions, while cascades predominantly consist of electromagnetic and hadronic showers.

@@

The event count for each bin reads
\begin{align}\label{eq:ICevents}
   N_{ij} &= T\sum_\beta \int_{(\zreco)_j}^{(\zreco)_{j+1}} \dd \zreco \int_{\Ereco_{i}}^{\Ereco_{i+1}} \dd \Ereco \int_0^\pi R(\theta^R,\theta^T) \dd \ztrue \int_0^\infty \phi_\beta^\text{det}(\Etrue,\theta^R)  A^\text{eff}(\Etrue) R(\Ereco,\Etrue) 
   \dd \Etrue\,,
\end{align}
where $T$ is the live time of the detector, and $A^\text{eff}$ its effective area obtained from~\cite{ICaeff}, in which $A^\text{eff}$ has been averaged over neutrinos and 
anti-neutrinos. $R(x^R,x^T)$ is a resolution function, 
which is responsible for the smearing between the reconstructed and true parameters $x^R$ and $x^T$, respectively. We assume a log-normal distribution, giving it the form 
\begin{align}
    R(x^R, x^T) = \frac{1}{\sqrt{2\pi} \sigma_{x^R}x^R} \exp\left[-\frac{(\log x^R-\mu(x^T))^2}{2\sigma_{x^R}^2}\right]\,.
\end{align}
However, the energy reconstruction is biased, meaning that the most probable reconstructed energy for a given true energy is not the same due to 
systematic differences~\cite{weaverThesis}. Thus, we don't assume that $\mu(\Etrue) =\Ereco$. 
To model this relationship between $\Etrue$ and $\Ereco$, we fit a Gaussian process regressor on the IC-86 Monte Carlo dataset from~\cite{IC2016}, from which
we can extract a predicted mean and standard deviation for a given $\Ereco$. We then take the $\Etrue$ points of the 99th percentile of each reconstructed
distribution to obtain the $\Etrue$ limits over which to integrate. We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like 
events is less than $\SI{2}{\degree}$, making $\ztrue$ practically coincide with $\zreco$ for our study~\cite{IC2020}.

\subsection{DeepCore}\label{ch:DCmethod}
We use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
IceCube collaboration in a $\nu_\mu$ disapprearance analysis~\cite{DC2018mudisappearance}.

@@

\subsection{PINGU}\label{ch:PINGUmethod}
The methodology behind the PINGU simulations is the same as with our DeepCore study~\ref{ch:DCmethod}. We use the public Monte Carlo~\cite{PINGUdata}, 
which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
However, since no detector systematics is yet modeled for PINGU, we take the correction factors $C_{ijk}$ are all unity. We will remedy this by including an uncorrelated systematic error,
which we can scale at will.
As with the DeepCore Monte Carlo, the PINGU Monte Carlo is divided into eight 
$\log_{10}\Ereco \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
We plot the normalized event differences $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for cascades and tracks in Fig.~\ref{fig:event_pulls}. %TODO:talk about this
We generate `data' by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.

@@

\subsection{Constraining the NSI parameters}\label{sec:constraining}
In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
For our analyses, we define our $\chi^2$ as
\begin{align} \label{eq:chisq}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin.

In our simulations of $N_{ijk}^\text{th}$, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, 
except for $\dm$ and $\theta_{23}$
which we vary over their $3\sigma$ limits \SIrange{2.435e-3}{2.598e-3}{\eV \squared} and \SIrange{40.1}{51.7}{\degree}, respectively.

We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
For IceCube, the event count takes the form
\begin{align}
    N^\text{th}_{ij} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ij}(\hat{\theta})\,,
\end{align}
with $N_{ij}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median cosine-zenith of $\zreco = -0.5$.

>>>>

\documentclass{article}
\newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{R})}}}
\newcommand{\ztrue}{\ensuremath{\cos{(\theta_z^{T})}}}
\newcommand{\emm}{\ensuremath{\epsilon_{\mu\mu}}}
\newcommand{\emt}{\ensuremath{\epsilon_{\mu\tau}}}
\newcommand{\eet}{\epsilon_{e\tau}}
\newcommand{\eem}{\epsilon_{e\mu}}
\newcommand{\ett}{\ensuremath{\epsilon_{\tau\tau}}}
\newcommand{\ep}{\ensuremath{\epsilon^\prime}}
\renewcommand{\ne}{\nu_e}
\newcommand{\Ereco}{E^{R}}
\newcommand{\Etrue}{E^{T}}
\newcommand{\nm}{\nu_\mu}
\newcommand{\ab}{\alpha\beta}
\newcommand{\nt}{\nu_\tau}
\newcommand{\ane}{\bar\nu_e}
\newcommand{\anm}{\bar\nu_\mu}               
\newcommand{\ant}{\bar\nu_\tau}
\newcommand{\dm}{\Delta m^2_{31}}
\newcommand{\sth}{\sin^2(2\theta_{23})}

\newcommand{\Pee}{P_{e  e}}
\newcommand{\Pem}{P_{e  \mu}}
\newcommand{\Pet}{P_{e  \tau}}

\newcommand{\Pme}{P_{\mu  e}}
\newcommand{\Pmm}{P_{\mu\mu}}
\newcommand{\Pmt}{P_{\mu  \tau}}

\newcommand{\Pte}{P_{P_{\tau e}}}
\newcommand{\Ptm}{P_{\tau  \mu}}
\newcommand{\Ptt}{P_{\tau  \tau}}

\newcommand{\Paeae}{P_{\bar{e}  \bar{e}}}
\newcommand{\Paeam}{P_{\bar{e}  \bar{\mu}}}
\newcommand{\Paeat}{P_{\bar{e}  \bar{\tau}}}

\newcommand{\Pamae}{P_{\bar{\mu}  \bar{e}}}
\newcommand{\Pamam}{P_{\bar{\mu}  \bar{\mu}}}
\newcommand{\Pamat}{P_{\bar{\mu}  \bar{\tau}}}

\newcommand{\Patae}{P_{\bar{\tau}  \bar{e}}}
\newcommand{\Patam}{P_{\bar{\tau}  \bar{\mu}}}
\newcommand{\Patat}{P_{\bar{\tau}  \bar{\tau}}}

\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\begin{document}
\section{Formalism of non-standard interactions}\label{sec:intro} %OK
Non-standard interactions are sub-leading contributions to neutrino flavor transitions arising from neutrino interactions not considered in the Standard Model.
We consider matter NSIs arising from the neutral current NSIs, which exclude production 
and detection effects. An effective four-fermion Lagrangian for this type of interaction can be written as
\begin{align}
   \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align}
where NC denotes the neutral current interaction with 
$f \in \{e,u,d\}$, and $P_X$ is the chirality projection operators with $X \in \{L,R\}$.

@@

We have no independent sensitivity for the chirality of $\epsilon^{fX}$, so we sum over these to obtain the vectorial parameter as $\epsilon^{fV}_{\alpha\beta} = \epsilon^{fL}_{\alpha\beta}+ \epsilon^{fR}_{\alpha\beta}$.
Moreover, we normalize the fermion number density $n_f$ by
the electron number density $n_e$. Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
so we use the relations $n_u/n_e \simeq n_d/n_e \simeq 3$.
The effective NSI parameters in matter now take the form
\begin{align} \label{eq:epsilon}
    \epsilon_{\alpha\beta} &= \sum_{X \in \{L,R\}} \sum_{f \in \{e,u,d\}} \frac{N_f}{N_e} \epsilon^{fX}_{\alpha\beta} \nonumber \\
                           &= \sum_X \epsilon_{\ab}^{eX} + 3(\epsilon_{\ab}^{uX} + \epsilon_{\ab}^{dX})
\end{align}
We note that our definition of $\epsilon_{\alpha\beta}$ differs from e.g. \cite{deepcoreNSI}, where the quark number density is used to normalize
the parameters.

@@

To propagate the neutrino states through the Earth, we solve the Schrödinger equation with the Hamiltonian from Eq.~\ref{eq:H_NSI}. 
The Earth density profile is taken from the PREM~\cite{PREM}, and we do not consider neutrino absorption.
The baseline for a given trajectory is determined using an average neutrino production height of 15 km and an Earth radius of 6371 km.
Thus, matter oscillations introduce a zenith angle dependence in two areas. Firstly, the matter potential depends on the matter density through the
neutrino propagates. A neutrino with $\cos{\theta_z} < -0.87$ will traverse through the dense Earth core, whereas a mantle-crossing neutrino 
with $\cos{\theta_z} > -0.87$ will not. Secondly, the zenith angle also alters the baseline through which a neutrino undergoes matter oscillations.
After this, we are ready to study the NSI effect on probability level.

\subsection{NSI phenomenology at probability level}\label{sec:nsiProbEffects} %OK
% Since neutrinos and antineutrinos have different cross sections, they are treated separately in the detector simulations. 
% However, for the purpose of qualitatively elucidating the NSI effect in this subsection, we take the effective area of $\nm$ and $\anm$ to be equal. 
% Thus, we simply add the neutrino to the antineutrino contributions in both Fig.~\ref{fig:nsi_probs} and Fig.~\ref{fig:flux_ratio}.

@@

% Due to the lightness of $\Delta m^2_{21}$, the $e$ channel has no resonance in the \si{\GeV} range. Thus, the only impact that 
% the NSI parameters considered here can have on any $\nu_e$ probability is shifting, and this only occurs when the requirements for the `double effect'
% are met. So except for the survival probability $P_{ee}$, any NSI parameter whose sector does not match the probability sector will not drastically affect it. 
% Thus, the only off-diagonal NSI parameters that strongly affect the transition probabilities $P_{\alpha\beta}$ are $\epsilon_{\gamma\beta}$,
% while the survival probabilities $P_{\alpha\alpha}$ are only strongly affected by $\epsilon_{\alpha\beta}$.

The atmospheric $\nm \to \nt$ transition will be the most abundant, making $\emt$, $\emm$, $\ett$ the most suitable
NSI parameters to constrain from muon events. As we will see, $\eem$ is also a good candidate to constrain, albeit a weaker one.

In Fig.~\ref{fig:emt_ett_probs}, we see how the introduction of $\emt = 0.02$ alters the $\nm$ and $\anm$ survival probabilities
for neutrinos that traverse the entire Earth diameter (i.e. $\ztrue = -1$). $\emt$ does not dramatically change neither
amplitude nor frequency of the probabilities. Instead, it seems to stretch or compress the oscillations. Since the 
only difference between the way neutrinos and antineutrinos interact with matter is the sign of the potential, the probability for
$\nm$ with positive $\epsilon_{\alpha\beta}$ is identical to the probability for $\anm$ with negative $\epsilon_{\alpha\beta}$. Thus, the dashed line 
in the right panel not only shows the survival probability for $\anm$ with $\emt=0.02$, but also the survival probability for $\nm$ with $\emt=-0.02$.
Hence, we note that $\emt > 0$ stretches (compresses) $\Pmm$ for neutrinos (antineutrinos), while $\emt < 0$ compresses (stretches) $\Pmm$ for neutrinos (antineutrinos).

The value of $\ett$ affects neither $\Pmm$ nor $\Pamam$, in the IceCube region above \SI{500}{\GeV}. Hence, we will not be able
to say anything about $\ett$ in our IceCube study.  Comparing the probabilities in Fig.~\ref{fig:emt_ett_probs} with $\ett = 0.05$ with the ones for $\emt = 0.02$ in Fig.~\ref{fig:emt_ett_probs},
we see that even though we let $\ett$ take 2.5 times the value of $\emt$, its effect on $\Pmm$ is smaller. The weakening of the $\Pamam$ resonance will be visible in DeepCore, but we should expect a less stringent 
constraint due to the weakness of the effect compared to $\emt$.

Thus, we will use IceCube to constrain $\emt$ only.

Moving on to $\eem$ and Fig.~\ref{fig:eem_eet_probs}, we see that both probabilities has shifted downwards for $\Etrue > \SI{500}{\GeV}$.
In Fig.~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The exception of this lies 
in the DeepCore region of rapid oscillations, where mixing is more violent. 
\begin{figure}
    \begin{center}
        \includegraphics[width=0.99\textwidth]{figures/Pmm_emt_probs.pdf}
        \includegraphics[width=0.99\textwidth]{figures/Pmm_ett_probs.pdf}
        \caption{\emph{Top panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\emt = 0.02$. All other NSI parameters are fixed to zero. In the \si{\GeV} range, $\emt$ shifts the oscillations to the right for $\nm$, and to the left for $\anm$. At \si{\TeV} energies, both probabilities simply get shifted down, resulting in a net reduction of track events.
        \emph{Bottom panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\ett = 0.05$. All other NSI parameters are fixed to zero. $\ett$ does not affect the probabilities above \SI{100}{\GeV} and this parameter is thus unable to be constrained by tracks in IceCube in our study. However, the dampening of the $\anm$ survival probability will be visible to DeepCore and PINGU, since it occurs within their energy ranges.}
        \label{fig:emt_ett_probs}
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics[width=0.99\textwidth]{figures/eem_probs.pdf}
        \includegraphics[width=0.99\textwidth]{figures/eet_probs.pdf}
        \caption{Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$. \emph{Top panel:} $\eem = 0.2$. All other NSI parameters are fixed to zero. Instead of the oscillations shifting to the left or right, $\eem$ dampens an oscillation peak for low \si{\GeV}. At \si{\TeV}, the probability is shifted down, just as with $\emt$.
        \emph{Bottom panel:} $\eet = 0.2$. All other NSI parameters are fixed to zero. Here, we see a very weak shifting and a $\nm$ weaker dip at low \si{\GeV}, and again, no visible effect at \si{TeV} energies. }
        \label{fig:eem_eet_probs}
    \end{center}
\end{figure}

\begin{figure}% TODO: check if this is redundant
   \includegraphics[width=0.85\textwidth]{figures/probabilities.pdf}
   \caption{}\label{fig:nsi_probs}
\end{figure}

The effect of NSI on the DeepCore event count has been previously discussed in~\cite{smirnovNSI}, while the NSI effect 
in PINGU has been studied in~\cite{choubey2014, ohlsson2013}.
Now we repeat our probability analysis but for the DeepCore/PINGU region of \SIrange{5.6}{56}{\GeV}. As we previously saw,
we have rapid oscillations, which means that `indirect' modifications (i.e. $\eet$ will affect the $\Pmm$ channel)
will be more apparent since all flavors are involved to a greater degree compared with the more stable region above \SI{500}{\GeV}, where 
many oscillations have averaged out.

Another feature of our DeepCore study includes the fact that we now have access to cascade events, in which $\ne$ and $\nt$ are more abundant.
Thus, we are no longer constrained to the $\mu$ channel alone, but we can now find interesting features in the other channels too. However, we 
remember that the $\nm$ flux is still the most abundant.

Fig.~\ref{fig:Pee_eet_probs} shows the electron neutrino and antineutrino survival probabilities, and here we see
a clear signal when turning on $\eet$.

\begin{figure}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{figures/Pee_eet_probs.pdf}
        \caption{Electron neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\eet = 0.2$. All other NSI parameters are fixed to zero. Here we see a strong difference across the whole energy range, in contrast to the $\nm$ and $\anm$ plots in Fig~\ref{fig:eem_eet_probs}.}
        \label{fig:Pee_eet_probs}
    \end{center}
\end{figure}

Fig.~\ref{fig:emt_ett_probs} shows that $\emt$ affects both $\Pmm$ and $\Pamam$ over the whole energy range. Since 
IceCube also sees this, we hope to be able to boost the constraining of $\emt$ by combining the two experiments.

Regarding $\ett$ in Fig.~\ref{fig:eem_eet_probs}, the signal mainly shows in the $\Pamam$ channel as
a shallower dip in the \SI{20}{\GeV} region. Thus, DeepCore/PINGU alone will be used to constrain this parameter.

$\eem$ in Fig.~\ref{fig:eem_eet_probs} causes a weaker dip for both $\nm$ and $\anm$.

For $\eet$, we see a similar effect on the dip in $\Pmm$ as we did with $\ett$ for $\Pamam$. Hence, we should be able to 
see the $\eet$ effect in DeepCore/PINGU. Remember that we now have the option to look at the other flavor channels than $\mu$ since we 
have cascade events for DeepCore and PINGU. If we simulate 
$\Pme^{NSI}$ at three different energies, and let both $\eem$ and $\eet$ vary together between the values $\{-0.3,0.3\}$, we produce a two-dimensional grid of probabilities.
Subtract the regular $\Pme^{SI}$ (that is, no NSI), and take the absolute value of the difference. We see the result in Fig.~\ref{fig:eem_eet_prob}. 
The middle and right panels, which show the absolute probability difference at \si{25} and $\SI{50}{\GeV}$, respectively, are very bleak,
indicating that the impact of the NSI parameters $\eem$ and $\eet$ is not as strong at these energy levels. Turning to the left-most panel,
we see a region in which the difference again is close to zero, but now surrounded by fringes of very large differences, up to $50\%$ difference 
in the $\Pme$ probability. This indicates that the NSI parameters are much more influential at these energies, and that we should be able to 
constrain both $\eem$ and $\eet$ from $\SI{5}{\GeV}$ cascade events.

\begin{figure}
    \centering
    \includegraphics[width=1\textwidth]{figures/eem_eet_prob.pdf}
    \caption{The quantity $\abs{P_{\mu e}^{NSI} - P_{\mu e}^{SI}}$ when we let $\eem$ and $\eet$ independently vary over
    the range \{-0.3,0.3\} at \si{5}, \si{25}, and $\SI{50}{\GeV}$. At $\SI{5}{\GeV}$, we see strong deviations in the probabilities, showing
    a promising indication that constriction of $\eem$ and $\eet$ is possible using cascade events at these energies.}\label{fig:eem_eet_prob}
\end{figure}

@@

\begin{figure}[!tb]
   \begin{center}
      \includegraphics[width=0.8\linewidth]{figures/flux_ratio.pdf}
   \end{center}
   \caption{Ratio of detector NSI to SI atmospheric $\nu_\mu + \bar{\nu}_\mu$ fluxes expressed as $(\phi_{\nu_\mu}^{NSI} + \phi_{\bar\nu_\mu}^{NSI})/(\phi_{\nu_\mu}^{SI} + \phi_{\bar\nu_\mu}^{SI})$.
   We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
   Left (right) panel shows the flux ratio in the energy range in which 99\% of the simulated DeepCore (IceCube) events are contained.
   }\label{fig:flux_ratio}
\end{figure}

\section{Detector formalism} %OK
The IceCube Neutrino Observatory is a gigaton Cherenkov detector located within Antarctic ice near the Geographic 
South Pole. It consists of 5160 individual digital optical modules situated on 86 strings, which detect Cherenkov light emitted by charged leptons
from neutrino events. We distinguish between two interaction topologies: track- and cascade-like events. Track-like events originate mainly
from muons originating from $\nm$ CC interactions, while cascades predominantly consist of electromagnetic and hadronic showers.

@@

The event count for each bin reads
\begin{align}\label{eq:ICevents}
    N_{ij} &= T \sum_\beta\int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r 
    \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \phi_\beta^\text{det}  A^\text{eff}_\beta \dd E^t
    \,,
\end{align}
where $T$ is the live time of the detector, $\beta$ the final neutrino flavors, $\theta_z^r$ the reconstructed 
zenith angle, i.e.~the deduced direction of the incoming neutrino binned with index $i$. $\theta^t_z$ is the true zenith angle of the incoming neutrino. 
$E^r$ is the reconstructed energy, binned with index $j$. $R(\theta^r,\theta^t)$ is a zenith resolution function 
that describes the relationship with the reconstructed and true zenith angles, specific to the 86-string configuration of IceCube.
$R(E^r,E^t)$ is an energy resolution function 
that describes the relationship with the reconstructed and true energies. $\phi_\beta^\text{det}$ is the conventional atmospheric neutrino flux for flavor $\beta$, propagated to detector level
in accordance with Eq.~\ref{eq:propFlux}. The effective area $A^\text{eff}$ is binned and provided to us by the IceCube collaboration~\cite{ICaeff}.

For the energy and zenith resolution functions, we assume a log-normal distribution, giving it the form 
\begin{align}
    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
\end{align}
However, the energy reconstruction is biased, meaning that the most probable reconstructed energy for a given true energy is not the same due to 
systematic differences~\cite{weaverThesis}. Thus, we don't assume that $\mu(\Etrue) =\Ereco$. 
To model this relationship between $\Etrue$ and $\Ereco$, we fit a Gaussian process regressor on the IC-86 Monte Carlo dataset from~\cite{IC2016}, from which
we can extract a predicted mean and standard deviation for a given $\Ereco$. We then take the $\Etrue$ points of the 99th percentile of each reconstructed
distribution to obtain the $\Etrue$ limits over which to integrate. We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like 
events is less than $\SI{2}{\degree}$, making $\ztrue$ practically coincide with $\zreco$ for our study~\cite{IC2020}.

\subsection{DeepCore}\label{ch:DCmethod} % OK
We use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
IceCube collaboration in a $\nu_\mu$ disapprearance analysis~\cite{DC2018mudisappearance}.

@@

\subsection{PINGU}\label{ch:PINGUmethod} % OK
The methodology behind the PINGU simulations is the same as with our DeepCore study~\ref{ch:DCmethod}. We use the public Monte Carlo~\cite{PINGUdata}, 
which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
However, since no detector systematics is yet modeled for PINGU,the correction factors $C_{ijk}$ are all unity. We will remedy this by including an uncorrelated systematic error,
which we can scale at will.
As with the DeepCore Monte Carlo, the PINGU Monte Carlo is divided into eight 
$\log_{10}\Ereco \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
We plot the normalized event differences $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for cascades and tracks in Fig.~\ref{fig:event_pulls}.
We generate `data' by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.

@@

\subsection{Constraining the NSI parameters}\label{sec:constraining} % Might need some shortening
In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
For our analyses, we define our $\chi^2$ as
\begin{align}\label{eq:chisq}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory in bin $\{i,j,k\}$, where $i$ denotes the $\Ereco$ bin, $j$ denotes the $\zreco$ bin,
and $k$ denotes the event-type bin, i.e. track or cascade. 
$N_{ijk}^\text{data}$ is the observed number of events in that bin. $\sigma^\text{data}_{ijk}$ is the experimental uncertainty, and $\sigma^\text{syst}_{ijk}$ the uncorrelated systematic
uncertainty.

In our simulations of $N_{ijk}^\text{th}$, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, 
except for $\dm[31]$ and $\theta_{23}$
which we vary over their $3\sigma$ limits \SIrange{2.435e-3}{2.598e-3}{\eV\squared} and \SIrange{40.1}{51.7}{\degree}, respectively~\cite{nufit}.

We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.05$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
For IceCube, the event count takes the form
\begin{align}
    N^\text{th}_{ij} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ij}(\hat{\theta})\,,
\end{align}
with $N_{ij}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median cosine-zenith of $\zreco = -0.5$.
